---
title: "1920s Car Stopping Distance"
author: "Clemens"
date: "7/22/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## 2: Overview

Do you have a 1920's car that you enjoy driving but aren't sure how long it will take you to stop?  Use this application to predict stopping distance from a speed based on data from the cars dataset in R.


## 3: Prediction Model Overview

This code shows an example of how the linear model is used to predict stopping distance (ft) from car speed (mph)

```{r, echo=TRUE}
speed <- 17
model <- lm(dist ~ speed, data = cars)
prediction <- predict(model, newdata = data.frame(speed))
```

The predicted stopping distance is:
```{r}
prediction
```

## 4: Example Plot Generation

Here is an example of the code for generating the resulting plot for a sample speed of 17 mph.  Note, this is reactive to a slider in the app

```{r, echo = TRUE, eval=FALSE}
speed <- 17
plot(cars$speed, cars$dist, xlab="Speed (MPH)", ylab="Stopping Distance (ft)", bty = "n", pch = 16)
abline(model, col = "red", lwd = 4)
points(speed, prediction, col = "red", pch=19,cex=4)
```

## 5: Example Plot 

This plot, which is reactive in the app, demonstrates the predicted stopping distance for a speed of 17 mph:
```{r}
plot(cars$speed, cars$dist, xlab="Speed (MPH)", ylab="Stopping Distance (ft)", bty = "n", pch = 16)
abline(model, col = "red", lwd = 4)
points(speed, prediction, col = "red", pch=19,cex=4)
```

Your plot is also showing your predicted stopping distance of:
```{r}
prediction
```

